\documentclass{seal_thesis}
% ---------------------- INSERT USED PACKAGES HERE ---------------------- 
\usepackage{xspace}
%\usepackage[usenames,dvipsnames]{xcolor}   
\usepackage[table,xcdraw]{xcolor}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\usepackage{url}
\usepackage{amsmath,mathtools}
\usepackage{graphicx, color}                                           
\usepackage{balance}                          
\usepackage{multirow}     
\usepackage{multicol}            
\usepackage{fancyvrb}     
\usepackage{tcolorbox}
\usepackage{tabularx,ragged2e} 
\usepackage{anyfontsize}
\usepackage{amsmath}
\usepackage[TABBOTCAP]{subfigure}                         
\usepackage{tikz}                  
\usepackage{paralist}   
\usepackage{booktabs}
\usepackage{float}

\input{macro}

% === Per gli snippet =====================================
\lstset{
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
%  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  deletekeywords={},			   % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  language=java,                      % the language of the code
  morekeywords={},            	   % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  tabsize=2                       % sets default tabsize to 2 spaces
%  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

% ---------------------- INSERT CUSTOMIZED COMMENTS HERE ---------------------- 
\newcommand\toolname[0]{BECLOMA}
\newcommand{\toolurl}{\url{https://bitbucket.org/sealuzh/becloma}}
\newcommand{\dynodroid}{\textsc{Dynodroid }}
\newcommand{\monkey}{\textsc{Monkey }}
\newcommand{\sapienz}{\textsc{Sapienz }}
\newcommand{\SessionLauncher}{\textsc{SessionLauncher}}
\newcommand{\FDroidCrawler}{\textsc{FDroidCrawler}}
\newcommand{\AppTester}{\textsc{AppTester}}
\newcommand{\Config}{\textsc{ConfigurationManager}}
\newcommand{\Cmd}{\textsc{CmdExecutor}}
\newcommand{\Stream}{\textsc{StreamGobbler}}
\newcommand{\Extractor}{\textsc{CrashLogExtractor}}
\newcommand{\Crash}{\textsc{CrashLog}}
\newcommand{\Lucene}{\textsc{LuceneTokenizer}}
\newcommand{\TFIDF}{\textsc{TFIDFCalculator}}
\newcommand{\Oracle}{\textsc{Oracle}}
\newcommand{\Review}{\textsc{Review}}
\newcommand{\ReviewC}{\textsc{ReviewCollector}}
\newcommand{\Linker}{\textsc{Linker}}
\newcommand{\Facade}{\textsc{SimilarityMetricsFacade}}
\newcommand{\Writer}{\textsc{Writer}}

% ---------------------- HERE STARTS THE THESIS BODY ---------------------- 
\thesisType{Bachelor Thesis}
\date{\today}
\title{Exploiting \vspace*{0.1em}User \vspace*{0.1em}Feedback \vspace*{0.1em}for Automated\vspace*{0.2em} Android Testing}
%\title{Exploiting User Feedback for Automated Android Testing}
%\title{Exploitation of User Feedback \vspace{0.25em} in the Automated Testing Process of \vspace{0.25em} Mobile Applications}
\subtitle{Toward User-Oriented Testing}
\author{Lucas Pelloni}
\home{18.03.1993, Zurich} % Geburtsort
\country{Switzerland}
\legi{13-722-038}
\prof{Prof. Dr. Harald C. Gall}
\assistent{Dr. Sebastiano Panichella \\ Giovanni Grano}
\email{lucas.pelloni@uzh.ch}
\urlT{https://bitbucket.org/sealuzh/becloma}
\begindate{08.01.2017}
\enddate{08.07.2017}

\begin{document}
\maketitle



\frontmatter


\input{citation}

\begin{acknowledgements}
The experience I lived with the implementation and subsequently the writing of my bachelor thesis has undoubtedly been one of the most rewarding academic experiences of my life until now. During these six months, I have learned to know the programming world more in depth, appreciating its challenges and its beauties more and more. However, the realization of my thesis would not have been possible without the help of some people. First, I would like to thank all those people who have contributed directly to the realization of my bachelor thesis. After that, those who indirectly allowed me to reach such an important goal of my life: my bachelors degree. 

First of all, I would like to express my deepest gratitude to my thesis advisor, Giovanni Grano. I would like to thank him for the patience he has shown during the past six months, for his guidance and support, for his constructive criticism and for having always encouraged me to achieve my best. I think one of the best things of my thesis was that he always allowed me to experiment and to be creative with the assigned tasks. I was able to "bang my head" against the new challenges, which helped me to find the right solutions. The final result of my thesis would not have been possible without his help. I would like to offer special thanks to Dr. Sebastiano Panichella for believing in me from the beginning and for giving me such a high-level thesis. Thanks for allowing me to discover a branch of computer science that I did not know in such detail before. I would also like to thank my two computer science schoolmates, Ile and Erion, who helped me a lot with their knowledge of android mobile devices. Finally, I would like to thank Professor Gall for giving me the opportunity to work together with the Software Evolution \& Architecture Lab at the University of Zurich, allowing me to use the most state-of-the-art infrastructures and technologies for my thesis. 

I would like to spend some words for those people, who have supported me during the whole bachelor degree. I would like to thank my parents for being there for me throughout all my bachelor track and for supporting me in times of need. I could never have done it without you and I hope you will be proud of me. 
%and I could explore it in a more practical way.
\end{acknowledgements}

\begin{abstract}
In the last years, the massive distribution of mobile devices like smartphones, tablets and more recently wearables, has radically changed our social life. Since the introduction of the first modern smartphone, the iPhone in 2007, we have witnessed a gradual shift from the traditional paradigm in the use of technology, entering the so called \textit{post-pc} era. Nowadays, the mobile market attracts always more developers and software firms. To sustain this fierce competition, they need to build high quality apps and at the same time, reach the market as soon as possible. It comes naturally to note that testing plays an important role in this process. Research focused for decades on traditional testing, aiming at reaching its maximum automation. However, automated testing for mobile applications presents different challenges and limitations that still need to be properly investigated. This thesis work tries to shed some initial light into possible solutions for such problems. In particular, we focused our attention on the knowledge that can be gained from mobile stores. Indeed, such stores represent an enormous amount of data easily available, like user reviews, and are an unmatched opportunity for software engineering research. Our final aim is to demonstrate how such user feedback can be in some way exploited to integrate and complement the state of art Android automated testing tools. Our results show that a noticeable set of problems can be actually detected only through user feedback. Such observation put the first stone down for a new paradigm of \textit{user oriented testing}.
We rely on the linking approach developed in this work in order to be able to enrich the generated crash logs with human-readable descriptions elicited from the connected user reviews. Therefore, we envision new generation of tools that are able to learn from such user reviews which are the components of a given mobile application to exercise more in depth, acting a sort of \textit{user-driven} prioritization of the testing effort.
\end{abstract}

%Wir verlassen uns, auf der in dieser Arbeit entwickelten Ansatz um die erzeugten Crash-Logs mit menschlichen lesbaren Beschreibungen bereichern zu können, die aus den angeschlossenen User Reviews hervorgerufen wurden.




\begin{zusammenfassung}
Durch die massive Zunahme der Verbreitung von Mobilfunkgeräten wie Smartphones, Tables und zuletzt Wearables, hast sich in den letzten Jahren unser Sozialverhalten drastisch geändert. Seit der Einführung des ersten "richtigen" Smartphones, des iPhones im Jahre 2007, wurden wir Zeuge eines allmählichen Wechsels von der traditionellen Technologienutzung hin zu dem, was man als "Post-PC-Ära" bezeichnet. Heutzutage wird der Mobilgerätemarkt für Entwickler und Softwarehäuser immer attraktiver. Um in diesem harten Wettbewerb mithalten zu können, müssen diese immer qualitativer hochwertigere Anwendungen (Apps) entwickeln und so schnell wie irgend möglich auf dem Markt anbieten. Von größter Wichtigkeit ist in diesem Prozess das Testing. Die Forschung fokussierte sich seit Jahrzehnten auf Standardtestverfahren mit dem Ziel, eine weitestgehende Automatisierung zu erreichen. Im Hinblick auf das Testing von Mobile Apps kommt dieses althergebrachte Testing aber an seine Grenzen und stellt neue Herausforderungen, die noch eingehend untersucht werden müssen. Diese Arbeit beschäftigt sich mit der Fragestellung, wie derartige Probleme einer Lösung zugeführt werden können. Im besonderen beschäftigen wir uns mit dem Know-how, welches recht einfach über Mobile-Stores verfügbar ist. Die enorme Menge an Daten und Informationen, die über Mobile-Stores frei verfügbar ist, erscheint uns bemerkenswert. Wir sprechen hier z. B. von User-Reviews, die eine bislang unübertroffene Quelle für Software Engineering Research darstellen. Unser Ziel ist es, darzustellen, wie das Feedback der User so ausgewertet werden kann, dass es ein wesentlicher und integraler Bestandteil der automatisierten Android-Testing-Tools wird.
Unsere Ergebnisse zeigen beeindruckend auf, dass eine beachtliche Menge von Problemen und Fehlern, nur allein durch das User-Feedabck gelöst werden konnte.Insofern legen diese Beobachtungen den Grundstein für eine neue Anschauung (Paradigma) des sogenannten \textit{User Oriented Testing}.
Wir sehen den in dieser Arbeit entwickelten Ansatz als hinreichend valide an, um die erzeugten Crash-Logs durch benutzerbasierte Beschreibungen bereichern zu können, die aus den angeführten User-Reviews generiert wurden.
Aus diesem Grunde, stellen wir eine neue Generation von Tools vor, die in der Lage ist, aus solchen zu "lernen", welche die Komponenten einer definierten mobilen App sind.
Dies deshalb, weil sie eine Form der \textit{benutzergesteuerten} Priorisierung des Testverfahrens darstellen.
\end{zusammenfassung}

\tableofcontents
\listoffigures
\listoftables
\lstlistoflistings

\mainmatter
\chapter{Introduction}
\label{sec:intro}
\input{intro}

\chapter{Related Work}
\label{sec:related}
\input{related_1}

\chapter{Approach}
\label{sec:approach}
\input{approach}

\chapter{\textbf{B}ug \textbf{E}xtractor, \textbf{C}lassifier and \textbf{L}inker \textbf{O}f \textbf{M}obile \textbf{A}pps}
\input{tool}

\chapter{Results and Discussion}
\input{result}

\chapter{Conclusions and Future Work}
\input{conclusion}




\backmatter
%alpha
\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}


%RQ2 -> risposta precisione table II paper 
%RQ3 -> IC, IR, IT -> fare leva sulle review per aumentare l'efficacia del testing 





